%%---------------------------------------------------------------------------%%
%%------------------------------ ╡н©╪ндов -----------------------------------%%
%%---------------------------------------------------------------------------%%


\begin{thebibliography}{30}

\bibitem{Candela1990} V. Candela and A. Marquina,
Recurrence Relations for Rational Cubic Methods I: The Halley
Method, Computing, 44 (1990) 169-184.

\bibitem{Deuflhard1979} Peter Deuflhard and G. Heindl, Affine
Invariant Convergence Theorems for Newton's Method and Extensions to
Related Methods, SIAM J. Numer. Anal., 16 (1979) 1-10.

\bibitem{Deuflhard2004} Peter Deuflhard, Newton Methods for
Nonlinear Problems: Affine Invariance and Adaptive Algorithms,
Springer-Verlag, Berlin Heidelberg, 2004.

\bibitem{Deuflhard1992} Peter Deuflhard and Florian A. Potra,
Asymptotic Mesh Independence of Newton-Galerkin Methods via a
Refined Mysovskii Theorem, SIAM J. Numer. Anal., 29 (1992)
1395-1412.

\bibitem{Ezquerro2005} J.A. Ezquerro and M.A. Hern\'{a}ndez, On
the R-Order of the Hally Method, J. Math. Anal. Appl., 303 (2005)
591-601.

\bibitem{Gutierrez1997} J.M. Guti\'{e}rrez and
M.A. Hern\'{a}ndez, Third-order Iterative Methods for Operators with
Bounded Second Derivative, J. Comput. Appl. Math., 82 (1997)
171-183.

\bibitem{Gutierrez2000} J.M. Guti\'{e}rrez and
M.A. Hern\'{a}ndez, Newton's Method under Weak Kantorovich
Conditions, IMA J. Numer. Anal., 20 (2000) 521-532.

\bibitem{Kantorvich1982} L.V. Kantorvich and G.P. Akilov,
Functional Analysis, Pergamon Press, Oxford, 1982.

\bibitem{Melman1997} A. Melman, Geometry and Convergence of Euler's
and Halley's Methods, SIAM Rev., 39 (1997) 728-735.

\bibitem{Wang2000} Xinghua Wang, Convergence of Newton's Method and
Uniqueness of the Solution of Equations in Banach Space, IMA J.
Numer. Anal., 20 (2000) 123-134.

\bibitem{WangLiLai2002} Xinghua Wang, Chong Li and Mingjun Lai, A
Unified Convergence Theory for Newton-Type Methods for Zeros of
Nonlinear Operators in Banach Spances, BIT, 42 (2002) 206-213.

\bibitem{Weiser2005} Martin Weiser, Anton Schiela and Peter
Deuflhard, Asymptotic Mesh Independence of Newton's Method
Revisited, SIAM J. Numer. Anal., 42 (2005) 1830-1845.

\bibitem{XuLi2007} Xiubin Xu and Chong Li, Convergence of
Newton's Method for Systems of Equations with Constant Rank
Derivatives, J. Comput. Math., 25 (2007) 705-718.

\bibitem{XuLi2008} Xiubin Xu and Chong Li, Convergence Criterion
of Newton's Method for Singular Systems with Constant Rank
Derivatives, J. Math. Anal. Appl., 345 (2008) 689-701.

\bibitem{Yao1999} Qingchuan Yao, On Halley Iteration, Numer. Math.,
81 (1999) 647-677.

\bibitem{YeLi2006} Xintao Ye, Chong Li, Convergence of the
Family of the Deformed Euler-Hally Iterations under the H\"{o}lder
Condition of the Second Derivative, J. Comput. Appl. Math., 194
(2006) 294-308.

\end{thebibliography}
