%%---------------------------------------------------------------------------%%
%%---------------------------- 中英文摘要 -----------------------------------%%
%%---------------------------------------------------------------------------%%



\begin{Abstract}
本文的主要内容是研究若干~Newton~型迭代算法
在计算一个给定矩阵的~$p$~次根时的收敛行为, 其中整数~$p\geq2$.
本论文的主要研究结果如下:



在第二章中,
基于~Iannazzo~\cite{Iannazzo2006,Iannazzo2008}~及~Guo~\cite{Guo2010}~研究~Newton~法收敛性所得到的结果,
我们进一步研究了~Newton~法在计算矩阵~$p$~次根的收敛行为,
得到了比现有结果更大的收敛域,
并证明了当给定矩阵的所有特征值都属于该收敛域时可以保证以单位矩阵为初始点的~Newton~法迭代产生的矩阵序列
收敛到该给定矩阵的主~$p$~次根, 且收敛速度是二阶的.


在第三章中, 我们研究了~Euler~法在计算矩阵~$p$~次根的收敛行为,
并得到了相应地收敛域,
同时我们亦证明了当给定矩阵的所有特征值都属于该收敛域时,
以单位矩阵为初始点,
由~Euler~法迭代产生的矩阵序列收敛于该矩阵的主~$p$~次根,
并且保持其快速的局部三阶收敛速度. 此外,
我们还讨论了~Euler~法的数值稳定性问题. 进一步,
我们同时也得到了关于~Halley~法的一个比~\cite{Iannazzo2008}~更好的收敛域,
在该收敛域中, 可以使~Halley~法仍然保持其局部的三阶收敛速度.



最后在第四章中, 根据所得到的三个迭代算法的收敛性结果,
结合~Schur~分解及矩阵平方根算法的计算优点,
我们给出了一个带有预处理的新的计算矩阵~$p$~次根的算法框架.
基于该框架, 选用不同的迭代法及相应的收敛域可以得到不同的算法. 然后,
通过若干的数值算例来验证所得到的收敛性结果在计算矩阵~$p$~次根时具有明显的优势.
特别地, 根据所得到的数值结果可以看出, 在计算矩阵~$p$~次根时,
Euler~法同~Newton~法和~Halley~法一样具有很好的计算效能,
且在多数情况下所需要的计算时间更少.

\Keywords{矩阵~$p$~次根; Newton~法; Halley~法; Euler~法; Schur~分解}
\end{Abstract}


\begin{EnglishAbstract}

This dissertation is concerned with the convergence behavior of some
Newton-type iterative methods for computing the principal $p$th root
of a given square matrix, where integer $p\geq2$.

In Chapter 2, we determine a new convergence region of Newton's
method for computing the principal $p$th root of a matrix. It is
shown that the Newton iteration starting from identity matrix will
converges to the principal $p$th root quadratically when all
eigenvalues of the matrix are in this new convergence region
including the one given in [C. Guo, On Newton's method and Halley's
method for the principal $p$th root of a matrix, Linear Algebra
Appl. 432 (2010) 1905-1922].

In Chapter 3, it is shown that the matrix sequence generated by
Euler iteration starting from identity matrix converges to the
principal $p$th root of a square matrix, if all eigenvalues of the
matrix are in a convergence region. The convergence is cubically if
the matrix is invertible. Meanwhile, we also show that for general
matrix when this iterative method does converge, it is usually
unstable. With the convergence analysis on Euler's method, we can
similarly give a convergence result for Halley's method.

And finally in Chapter 4, by using a preprocessing as in [C. Guo and
N. J. Higham, A Schur-Newton method for the matrix $p$th root and
its inverse, SIAM J. Matrix Anal. Appl. 28 (2006) 788-804], we give
a framework that computes the principal $p$th root of a matrix by
using Schur decomposition and some iterative method. A number of
modifications to this framework are possible. Numerical experiments
show that the obtained convergence results are better than the
existing ones and that Euler's method has the same excellent
numerical behavior as Newton's  and Halley's methods, and suggest
that Euler's method is also a good choice for computing matrix $p$th
root.

\EnglishKeywords{Matrix $p$th root; Newton's method; Halley's
method; Euler's method; Schur decomposition}
\end{EnglishAbstract}
